Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-19 ms.tex
added column for per-band nominal detector noise to table of basic map parameters

\begin{deluxetable*}{rrrrrr} 
\tabletypesize{\scriptsize}
\tablecolumns{5} 
\tablewidth{0pc} 
\tablecaption{\label{table:offs} Planck/IRAS Map Properties \& Pre-processing} 
\tablehead{
\colhead{$\nu$ (GHz)} &
\colhead{Offset ($K_{CMB}$)} & 
\colhead{Dipole ($K_{CMB}$)} & 
\colhead{$c_{\nu}$} &
\colhead{FWHM ($'$)}
}
\startdata
100 & 1.69$\times$10$^{-5}$$\pm$3.61$\times$10$^{-7}$ & $-$1.08$\times$10$^{-5}$ &  0.0054 & 9.66 \\
143 & 3.58$\times$10$^{-5}$$\pm$7.58$\times$10$^{-7}$ & $-$1.08$\times$10$^{-5}$ & 0.0054 &  7.27 \\
217 & 7.79$\times$10$^{-5}$$\pm$2.60$\times$10$^{-6}$ & $-$1.40$\times$10$^{-5}$ & 0.0054 &  5.01 \\
353 & 2.76$\times$10$^{-4}$$\pm$1.95$\times$10$^{-5}$ & $-$3.08$\times$10$^{-5}$ & 0.012 & 4.86 \\
    & Offset (MJy/sr) & Dipole (MJy/sr) & & \\ \cline{2-3} \\ [-2ex]
545 & 7.27$\times$10$^{-2}$$\pm$1.99$\times$10$^{-2}$ & 1.63$\times$10$^{-2}$ & 0.10 & 4.84 \\
857 & 1.82$\times$10$^{-2}$$\pm$6.02$\times$10$^{-2}$ &  - & 0.10 & 4.63 \\
3000 & 0.0$\pm$4.3$\times$10$^{-2}$ & - & 0.10 & 6.1
\enddata
\end{deluxetable*}

>>>>

\begin{deluxetable*}{cccccc} 
\tabletypesize{\scriptsize}
\tablecolumns{6} 
\tablewidth{0pc} 
\tablecaption{\label{table:offs} Planck/IRAS Map Properties \& Pre-processing} 
\tablehead{
\colhead{$\nu$ (GHz)} &
\colhead{Offset ($K_{CMB}$)} & 
\colhead{Dipole ($K_{CMB}$)} & 
\colhead{$n_{\nu}$} ($K_{CMB}$) &
\colhead{$c_{\nu}$} &
\colhead{FWHM ($'$)} 
}
\startdata
100  & 1.69$\times$10$^{-5}$$\pm$3.61$\times$10$^{-7}$ & $-$1.08$\times$10$^{-5}$ & 7.77$\times$10$^{-5}$ & 0.0054 & 9.66 \\
143  & 3.58$\times$10$^{-5}$$\pm$7.58$\times$10$^{-7}$ & $-$1.08$\times$10$^{-5}$ & 3.25$\times$10$^{-5}$ & 0.0054 & 7.27 \\
217  & 7.79$\times$10$^{-5}$$\pm$2.60$\times$10$^{-6}$ & $-$1.40$\times$10$^{-5}$ & 4.51$\times$10$^{-5}$ & 0.0054 & 5.01 \\
353  & 2.76$\times$10$^{-4}$$\pm$1.95$\times$10$^{-5}$ & $-$3.08$\times$10$^{-5}$ & 1.51$\times$10$^{-4}$ & 0.012  & 4.86 \\
     & Offset (MJy/sr)                                 & Dipole (MJy/sr)          & $n_{\nu}$ (MJy/sr)    &        &      \\ \cline{2-4} \\ [-2ex]
545  & 7.27$\times$10$^{-2}$$\pm$1.99$\times$10$^{-2}$ & 1.63$\times$10$^{-2}$    & 0.046                 & 0.10   & 4.84 \\
857  & 1.82$\times$10$^{-2}$$\pm$6.02$\times$10$^{-2}$ & -                        & 0.046                 & 0.10   & 4.63 \\
3000 & 0.0$\pm$4.3$\times$10$^{-2}$                    & -                        & 0.06                  & 0.10   & 6.1
\enddata
\end{deluxetable*}
